---
title: "Barkan etal (2012) data analysis using raw data - V1"
author: "Yvonne JIN"
date: "7/19/2022"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

## Download packages and load packages
list.of.packages <- c("haven", "dplyr", "tidyverse", "jmv", "apaTables", "arsenal", "ggstatsplot","QuantPsyc")

new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, dependencies = TRUE)

invisible(lapply(list.of.packages, library, character.only = TRUE))

Sys.setenv(LANG = "en")
options(scipen=999.99, digits =5)

# update all packages
# update.packages() 

# a tweak to point RStudio to the current directory of the R file
# this.dir <- dirname(rstudioapi::getActiveDocumentContext()$path)
# setwd(this.dir)
```

```{r read data}
df <- read_sav("RRR-Barkan-etal-2012-WITH-order.sav")
colnames(df)
df_recall <- df %>% dplyr::select("RecallComprDissoWri":"Recall_Check2_negati")
```

# Study response processing

## participant screening
Screen out those not met the pre-survey validation questions.
```{R screening}

# screen out the participants flagged as likely to be bots or duplicates
# criteria provided by Qualtrics: https://www.qualtrics.com/support/survey-platform/survey-module/survey-checker/fraud-detection/
df <- df %>% filter(Q_RecaptchaScore >= 0.5 & Q_RelevantIDDuplicate != "true" & Q_RelevantIDDuplicateScore < 75 & Q_RelevantIDFraudScore <30)
#1050 -> 986

# screen out the participants not agreed to the validation questions before survey
df <- df %>% filter(consentagree_1 == 1 & outline1 == 1 & outline2 == 1 & englishnative == 1 & writing_check == 1)
# 986 -> 930

# check distribution of survey duration
hist(df$Duration__in_seconds_)
summary(df$Duration__in_seconds_)

# will screen out the partcipants that fail to answer the validation question of recall manipulation in the "Condition marking" section below.
```
General measurements score calculation: Manipulation check and MASC uses averaged score of individual items.

## Manipulation Check - Self Esteem Scale
```{r Mani Check average score, echo=TRUE}
df$ManiCheck <- df %>% dplyr::select(starts_with("ManiCheck")) %>% rowMeans()
# Add package name before function "select" 
# to prevent confusion with same name functions in other packages
```

## Study 3 MASC - Multi Aspect Scale of Cheating
```{r MASC average score}
df$MASC_set1 <- df %>% dplyr::select(starts_with("MASC_set1")) %>% rowMeans()
df$MASC_set2 <- df %>% dplyr::select(starts_with("MASC_set2")) %>% rowMeans()
df$MASC_set3 <- df %>% dplyr::select(starts_with("MASC_set3")) %>% rowMeans()
```

## Study 3 BIDR - The Balanced Inventory of Desirable Responding
Scoring: 
Respondents are asked to rate the 40-items on a 7 point scale according to their level of agreement with the item (stated as propositions). 
The scoring key is balanced. All even number statements of self-deceptive positivity (former 20 statements) are negatively keyed. All odd number statements of impression management (latter 20 statements) are negatively keyed. After reversing the negatively keyed items, one point is added for each extreme response (6 or 7). 
Total scores on the both constructs can range from 0 to 20. Thus, high scores are only attained by respondents who give exaggeratedly desirable responses. All 40 items may be summed to give an overall measure of social desirable responding.

```{r BIDR}
#-------------------------------#
### self deceptive positivity

# positively keyed statements
BIDR_self_deceptive_odd <- df %>% 
  dplyr::select("BIDR_Self_deceptive_2","BIDR_Self_deceptive_4","BIDR_Self_deceptive_6",
                "BIDR_Self_deceptive_8","BIDR_Self_deceptive_10","BIDR_Self_deceptive_12",
                "BIDR_Self_deceptive_14","BIDR_Self_deceptive_16","BIDR_Self_deceptive_18",
                "BIDR_Self_deceptive_20")
# iterate the item to avoid counting variables like"BIDR_Self_deceptive_DO_20"

BIDR_self_deceptive_odd_recode <- as.data.frame(ifelse(BIDR_self_deceptive_odd > 5, 1,0))

# negatively keyed statements
BIDR_self_deceptive_even <- df %>% 
  dplyr::select("BIDR_Self_deceptive_1","BIDR_Self_deceptive_3","BIDR_Self_deceptive_5",
                "BIDR_Self_deceptive_7","BIDR_Self_deceptive_9","BIDR_Self_deceptive_11",
                "BIDR_Self_deceptive_13","BIDR_Self_deceptive_15","BIDR_Self_deceptive_17",
                "BIDR_Self_deceptive_19")

BIDR_self_deceptive_even_recode <- as.data.frame(ifelse(BIDR_self_deceptive_even < 3, 1,0))

#----------------------------#
###  impression management

# positively keyed statements
BIDR_impre_manage_even <- df %>% 
  dplyr::select("BIDR_Impre_manage_2","BIDR_Impre_manage_4","BIDR_Impre_manage_6",
                "BIDR_Impre_manage_8","BIDR_Impre_manage_10","BIDR_Impre_manage_12",
                "BIDR_Impre_manage_14","BIDR_Impre_manage_16","BIDR_Impre_manage_18",
                "BIDR_Impre_manage_20")

BIDR_impre_manage_even_recode <- as.data.frame(ifelse(BIDR_impre_manage_even > 5, 1,0))

# negatively keyed statements 
BIDR_impre_manage_odd <- df %>% 
  dplyr::select("BIDR_Impre_manage_1","BIDR_Impre_manage_3","BIDR_Impre_manage_5",
                "BIDR_Impre_manage_7","BIDR_Impre_manage_9","BIDR_Impre_manage_11",
                "BIDR_Impre_manage_13","BIDR_Impre_manage_15","BIDR_Impre_manage_17",
                "BIDR_Impre_manage_19") 
# iterate the item to avoid counting variables like"BIDR_Impre_manage_DO_11"

BIDR_impre_manage_odd_recode <- as.data.frame(ifelse(BIDR_impre_manage_odd < 3, 1,0))


#------------------------------------------#
# merge all recoded score into one dataframe

recode_BIDR_self_deceptive <- BIDR_self_deceptive_odd_recode %>% 
  cbind(BIDR_self_deceptive_even_recode) 

recode_BIDR_impre_manage <- BIDR_impre_manage_odd_recode %>%
  cbind(BIDR_impre_manage_even_recode) 

# add up recoded score to form an overall score, add to main dataframe
df$BIDR_self_deceptive <- recode_BIDR_self_deceptive  %>% rowSums()
df$BIDR_impre_manage <- recode_BIDR_impre_manage  %>% rowSums()

```

## Condition marking

Conditions allocated for each participants and the order of experiments presented are marked in Qualtrics by variables starting with "FL".
```{r survey block order}
# find block order of conditions
block_order <- df %>% dplyr::select(starts_with("FL"))
colnames(block_order)
```

```{r mark study order}
# Mark study presentation order
df$study_order = ifelse(df$FL_11_DO_Experiment1_HiringDecisionasHR == 1,"Exp1First","Exp2First")
```

Slicing dataframe into five recall conditions. 
```{r recall conditions }

## ethical dissonance & writing response 
ethi_dis_write <- df %>% filter(FL_9_DO_RecallManipulation_EthicalDissonancebyWriting_UnethicalB == 1) %>%
  dplyr::select(RecallComprDissoWri:RecallCheck2DissoWri, # recall manipulation and comprehension check
         "study_order",
         "ManiCheck", # precalculated average
         starts_with("Exp1"),
         starts_with("Exp2"),
         "MASC_set1", "MASC_set2", "MASC_set3", # precalculated average
         "BIDR_self_deceptive","BIDR_impre_manage", # precalculated
         age:CountryName, Duration__in_seconds_) %>% #demographic data and condition marker
  mutate(condition = "Dissonance_write")

ethi_dis_write <- ethi_dis_write %>% filter(RecallComprDissoWri == 1 & RecallCheck2DissoWri == 1)

## ethical dissonance & writing response 
ethi_dis_nowrite <- df %>% filter(FL_9_DO_RecallManipulation_EthicalDissonanceWithoutWriting == 1) %>%
  dplyr::select(RecallComprDissNWri:RecallCheck2DissNWri,
         "study_order",
         "ManiCheck", 
         starts_with("Exp1"),
         starts_with("Exp2"),
         "MASC_set1", "MASC_set2", "MASC_set3", 
         "BIDR_self_deceptive","BIDR_impre_manage", 
         age:CountryName, Duration__in_seconds_) %>% 
  mutate(condition = "Dissonance_no_write")

ethi_dis_nowrite <- ethi_dis_nowrite %>% filter(RecallComprDissNWri == 1 & RecallCheck2DissNWri == 1)

## control: worthy conduct
con_worthy <- df %>% filter(FL_9_DO_RecallManipulation_WorthyConduct == 1) %>%
  dplyr::select(RecallComprehWorthy:Recall_Check2_Worthy,
         "study_order",
         "ManiCheck",
         starts_with("Exp1"),
         starts_with("Exp2"),
         "MASC_set1", "MASC_set2", "MASC_set3",
         "BIDR_self_deceptive","BIDR_impre_manage",
         age:CountryName, Duration__in_seconds_) %>%
  mutate(condition = "Worthy") # control condition: worthy conduct

con_worthy <- con_worthy %>% filter(RecallComprehWorthy == 4 & Recall_Check2_Worthy == 2)

## control: neutral event
con_neutral <- df %>% filter(FL_9_DO_RecallManipulation_Neutral == 1) %>%
  dplyr::select(Recall_Compr_Neutral:Recall_Check2_neutra,
         "study_order",
         "ManiCheck",
         starts_with("Exp1"),
         starts_with("Exp2"),
         "MASC_set1", "MASC_set2", "MASC_set3",
         "BIDR_self_deceptive","BIDR_impre_manage",
         age:CountryName, Duration__in_seconds_) %>% 
  mutate(condition = "Neutral") # control condition: Neutral behavior

hist(con_neutral$Recall_Check2_neutra)
# more than 70 participants chose 2: Happy / Fulfilled / Wholesome instead of 4: Normal / Peaceful / As usual
#con_neutral <- con_neutral %>% filter(Recall_Compr_Neutral == 2 & (Recall_Check2_neutra == 4 | Recall_Check2_neutra == 2) )

con_neutral <- con_neutral %>% filter(Recall_Compr_Neutral == 2 & Recall_Check2_neutra == 4 )

## control: negative event
con_nega <- df %>% filter(FL_9_DO_RecallManipulation_NegativeValence ==1) %>%
  dplyr::select(Recall_Compr_negativ:Recall_Check2_negati,
         "study_order",
         "ManiCheck",
         starts_with("Exp1"),
         starts_with("Exp2"),
         "MASC_set1", "MASC_set2", "MASC_set3",
         "BIDR_self_deceptive","BIDR_impre_manage",
         age:CountryName, Duration__in_seconds_) %>%
  mutate(condition = "Negative") # control condition: negative valence

con_nega <- con_nega %>% filter(Recall_Compr_negativ == 3 & Recall_Check2_negati == 3)
# overlap between 1 (unethical) and 3 (negative emotions)?

```

Combine data segments with condition marking. 
```{r combine processed variables}
cleaned_df <- ethi_dis_write[5:43] %>% 
  rbind(ethi_dis_nowrite[5:43]) %>%
  rbind(con_worthy[5:43]) %>%
  rbind(con_neutral[5:43]) %>%
  rbind(con_nega[5:43]) 
# 930 -> 765
colnames(cleaned_df)

# check distribution of survey duration in the cleaned dataset 
hist(cleaned_df$Duration__in_seconds_)
summary(cleaned_df$Duration__in_seconds_)
```
# Response formatting for study 1 and study 2 DVs
Change the data type of DVs to numeric, so the ANOVA test and ggstatsplot works properly.
```{r}
DVs <- c("Exp1_prob_hiring", "Exp1_loyalty","Exp1_honesty", "Exp2_S1_seen_wrong", "Exp2_S1_self_action", "Exp2_S1_guide_other", "Exp2_S2F_seen_wrong", "Exp2_S2F_self_action", "Exp2_S2F_guide_other", "Exp2_S2M_seen_wrong", "Exp2_S2M_self_action","Exp2_S2M_guide_other")
cleaned_df[DVs] <- sapply(cleaned_df[DVs],as.numeric)
```

Merge study 2 scenario 2, female and male case together.
```{r combine gendered conditions}

cleaned_df$Exp2_S2_seen_wrong_T2 = coalesce(cleaned_df$Exp2_S2F_seen_wrong,cleaned_df$Exp2_S2M_seen_wrong)
cleaned_df$Exp2_S2_self_action_T2 = coalesce(cleaned_df$Exp2_S2F_self_action,cleaned_df$Exp2_S2M_self_action)
cleaned_df$Exp2_S2_guide_other_T2 = coalesce(cleaned_df$Exp2_S2F_guide_other,cleaned_df$Exp2_S2M_guide_other)

```

```{r output processed data}
# output cleaned data
write.csv(cleaned_df, "cleaned_data_0719_screened_812.csv",fileEncoding = "UTF-8")
```

# Descriptive data
```{r descriptives}
# Manipulation Check
## overall
jmv::descriptives(data = cleaned_df, vars = vars(ManiCheck)) 
## by condition
jmv::descriptives(
    formula = ManiCheck ~ condition,
    data = cleaned_df,
    missing = FALSE,
    median = FALSE,
    variance = TRUE,
    min = FALSE,
    max = FALSE,
    ci = TRUE) 


# Study 1
## total
jmv::descriptives(data = cleaned_df, vars = vars(Exp1_prob_hiring, Exp1_loyalty, Exp1_honesty))
## by condition
jmv::descriptives(
    formula = Exp1_prob_hiring + Exp1_loyalty + Exp1_honesty ~ condition,
    data = cleaned_df,
    missing = FALSE, median = FALSE)

# Study 2 scenario 1
## total
jmv::descriptives(
    data = cleaned_df,
    vars = vars(Exp2_S1_seen_wrong, Exp2_S1_self_action, Exp2_S1_guide_other),
    missing = FALSE, median = FALSE)
## by condition
jmv::descriptives(
    formula = Exp2_S1_seen_wrong + Exp2_S1_self_action + Exp2_S1_guide_other ~ condition,
    data = cleaned_df,
    missing = FALSE, median = FALSE)

# Study scenario 2
## total 
jmv::descriptives(
    data = cleaned_df,
    vars = vars(Exp2_S2_seen_wrong_T2, Exp2_S2_self_action_T2, Exp2_S2_guide_other_T2),
    missing = FALSE, median = FALSE)
## by condition
jmv::descriptives(
    formula = Exp2_S2_seen_wrong_T2 + Exp2_S2_self_action_T2 + Exp2_S2_guide_other_T2 ~ condition,
    data = cleaned_df,
    missing = FALSE, median = FALSE)

# Study 3
## total
jmv::descriptives(
    data = cleaned_df,
    vars = vars(MASC_set1, MASC_set2, MASC_set3, BIDR_self_deceptive, BIDR_impre_manage))
## condition
jmv::descriptives(
    formula = MASC_set1 + MASC_set2 + MASC_set3 + BIDR_self_deceptive + BIDR_impre_manage ~ condition,
    data = cleaned_df,
    missing = FALSE, median = FALSE)

# Age and Gender distribution
jmv::descriptives(
    data = cleaned_df,
    vars = vars(age, gender))

# plot descriptive table
#tableby.control()
#table_one <- tableby(age ~ ., data = cleaned_df) 
#table_one
#summary(table_one, title = "Descriptive Data")


```

# Planned Analysis - Main Analysis 

## Manipulation check - ANOVA

```{r Manipulation check}

jmv::ANOVA(
    formula = ManiCheck ~ condition,
    data = cleaned_df,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    #emMeans = ~ condition,
    emmTables = TRUE)

# plot the APA style table 
ANOVA_mani_check <- lm(ManiCheck ~ condition, data = cleaned_df)

# plot ggstatsplot and save
ggstatsplot::ggbetweenstats(
    data = cleaned_df,
    y = ManiCheck,
    x = condition,
    originaltheme = TRUE,
    ylab = "Manipulation Check",
    xlab = "Conditions")

```

```{R ManiCheck output, echo=TRUE}
# save the table and plot to local folder. Might interrupt with knitting, hence disabled after export.

apa.aov.table(ANOVA_mani_check, filename = "Manipulation check ANOVA.doc",table.number = 1)
ggsave(
  "ManipulationCheck_plot.png",
  plot = last_plot(),
  width = 9, height = 5.5,
  dpi = 600)

```
## Study 1 - ANOVA

Study 1 DV1 - Likelihood of Hiring the canditate with ethically questionable behavior.
```{r S1 ANOVA DV1}
jmv::ANOVA(
    formula = Exp1_prob_hiring ~ condition,
    data = cleaned_df,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    emmTables = TRUE)

ANOVA_Study1_DV1 <- lm(Exp1_prob_hiring ~ condition, data = cleaned_df)

# plot ggstatsplot and save
ggstatsplot::ggbetweenstats(
    data = cleaned_df,
    y = Exp1_prob_hiring,
    x = condition,
    originaltheme = TRUE,
    ylab = "Study 1 Likelihood of hiring",
    xlab = "Conditions")

```

```{R study1DV1 outout, echo=TRUE}
apa.aov.table(ANOVA_Study1_DV1, filename = "Exp1 DV1 ANOVA.doc",table.number = 2)
ggsave(
  "Study1DV1Hiring.png", plot = last_plot(),
  width = 9, height = 5.5, dpi = 600)
```

Study 1 DV2 - Perceived Loyalty to company if the candidate is hired.
```{R S1 ANOVA DV2, echo=TRUE}
jmv::ANOVA(
    formula = Exp1_loyalty ~ condition,
    data = cleaned_df,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    emmTables = TRUE)

ANOVA_exp1_DV2 <- lm(Exp1_loyalty ~ condition, data = cleaned_df)

# plot ggstatsplot and save
ggstatsplot::ggbetweenstats(
    data = cleaned_df,
    y = Exp1_loyalty,
    x = condition,
    originaltheme = TRUE,
    ylab = "Study 1 Perceived Loyalty",
    xlab = "Conditions")
```

```{R Study1DV2 output, echo=TRUE}

apa.aov.table(ANOVA_exp1_DV2, filename = "Exp1 DV2 ANOVA.doc",table.number = 3)
ggsave(
  "Study1DV2Loyalty.png", plot = last_plot(),
  width = 9, height = 5.5, dpi = 600)

```

Study 1 DV3 - Perceived honesty of the candidate.
```{r S1 ANOVA DV3}
jmv::ANOVA(
    formula = Exp1_honesty ~ condition,
    data = cleaned_df,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    emmTables = TRUE)

ANOVA_exp1_DV3 <- lm(Exp1_honesty ~ condition, data = cleaned_df)

# plot ggstatsplot and save
ggstatsplot::ggbetweenstats(
    data = cleaned_df,
    y = Exp1_honesty,
    x = condition,
    originaltheme = TRUE,
    ylab = "Study 1 Perceived Honesty",
    xlab = "Conditions")
```

```{R Study1DV3 output, echo=TRUE}
apa.aov.table(ANOVA_exp1_DV3, filename = "Exp1 DV3 ANOVA.doc",table.number = 4)
ggsave(
  "Study1DV3Honesty.png", plot = last_plot(),
  width = 9, height = 5.5, dpi = 600)
```

## Study 2 - Repeated ANOVA

Pivot to long format for ggstatsplot.
```{r study 2 pivot longer, echo=TRUE}
# add a column of unique participant ID
cleaned_df <- dplyr::mutate(cleaned_df, ID = row_number())

#pivot longer
df_s2DV1 <- pivot_longer(cleaned_df, cols = c(Exp2_S1_seen_wrong, Exp2_S2_seen_wrong_T2),names_to = "scenario",values_to = "Exp2_seen_wrong") 
df_s2DV2 <- pivot_longer(cleaned_df, cols = c(Exp2_S1_self_action, Exp2_S2_self_action_T2),names_to = "scenario",values_to = "Exp2_self_action") 
df_s2DV3<- pivot_longer(cleaned_df, cols = c(Exp2_S1_guide_other, Exp2_S2_guide_other_T2),names_to = "scenario",values_to = "Exp2_guide_other") 

# combine three DVs
df_s2long <- df_s2DV1 %>% dplyr::select("ID","condition","scenario","Exp2_seen_wrong") %>% dplyr::mutate(Exp2_seen_wrong = as.numeric(Exp2_seen_wrong)) %>%
  cbind(Exp2_self_action = as.numeric(df_s2DV2$Exp2_self_action)) %>%
  cbind(Exp2_guide_other = as.numeric(df_s2DV3$Exp2_guide_other))

# rename the scenario variable for plotting 
df_s2long <- df_s2long %>% 
  mutate(scenario = case_when(
    scenario == "Exp2_S1_seen_wrong" ~ "Scenario 1 Leaking interview questions",
    scenario == "Exp2_S2_seen_wrong_T2" ~ "Scenario 2 Changing used product"))

```

Study 2 DV2 - Perception of suggested actions as wrong.
```{r S2 DV1 ANOVA}

jmv::anovaRM(
    data = cleaned_df,
    rm = list(
        list(
            label="scenario",
            levels=c("S1", "S2"))),
    rmCells = list(
        list(
            measure="Exp2_S1_seen_wrong",
            cell="S1"),
        list(
            measure="Exp2_S2_seen_wrong_T2",
            cell="S2")),
    bs = condition,
    effectSize = "eta",
    rmTerms = ~ scenario,
    bsTerms = ~ condition,
    leveneTest = TRUE,
    #emMeans = ~ scenario:condition,
    emmTables = TRUE,
    groupSumm = TRUE)

# ggstatsplot for condition comparisons in between-subjects designs repeated across all levels of a grouping variable.
# link to tutorial: https://indrajeetpatil.github.io/ggstatsplot/reference/grouped_ggbetweenstats.html

ggstatsplot::grouped_ggbetweenstats(
  data = df_s2long,
  y = Exp2_seen_wrong,
  x = condition,
  grouping.var = scenario,
  ylab = "Perceived unethicality",
  xlab = "Conditions"
  ) 
```

```{R Study2DV1 plot, echo=TRUE}
ggsave(
  "Study2DV1SeenWrong.png", plot = last_plot(),
  width = 11.8, height = 6, dpi = 600)

```

Study 2 DV2 - Likelihood of the self conducting similar behavior.
```{r S2 DV2 ANOVA}
jmv::anovaRM(
    data = cleaned_df,
    rm = list(
        list(
            label="scenario",
            levels=c("S1", "S2"))),
    rmCells = list(
        list(
            measure="Exp2_S1_self_action",
            cell="S1"),
        list(
            measure="Exp2_S2_self_action_T2",
            cell="S2")),
    bs = condition,
    effectSize = "eta",
    rmTerms = ~ scenario,
    bsTerms = ~ condition,
    leveneTest = TRUE,
    #emMeans = ~ scenario:condition,
    emmTables = TRUE,
    groupSumm = TRUE)

ggstatsplot::grouped_ggbetweenstats(
  data = df_s2long,
  y = Exp2_self_action,
  x = condition,
  grouping.var = scenario,
  ylab = "Likelihood of the self conducting suggested behavior",
  xlab = "Conditions"
  ) 

```

```{R Study2DV2 plot, echo=TRUE}
ggsave(
  "Study2DV2SelfAction.png", plot = last_plot(),
  width = 11.8, height = 6, dpi = 600)

```

Study 2 DV3 - Likelihood of advising others to perform unethical but self-benefiting behavior.
```{r S2 DV3 ANOVA}
jmv::anovaRM(
    data = cleaned_df,
    rm = list(
        list(
            label="scenario",
            levels=c("S1", "S2"))),
    rmCells = list(
        list(
            measure="Exp2_S1_guide_other",
            cell="S1"),
        list(
            measure="Exp2_S2_guide_other_T2",
            cell="S2")),
    bs = condition,
    effectSize = "eta",
    rmTerms = ~ scenario,
    bsTerms = ~ condition,
    leveneTest = TRUE,
    #emMeans = ~ scenario:condition,
    emmTables = TRUE,
    groupSumm = TRUE)

ggstatsplot::grouped_ggbetweenstats(
  data = df_s2long,
  y = Exp2_guide_other,
  x = condition,
  grouping.var = scenario,
  ylab = "Likelihood of advising others to behave unethically",
  xlab = "Conditions"
  ) 
```

```{R Study2DV3 plot, echo=TRUE}
ggsave(
  "Study2DV3AdviseOthers.png", plot = last_plot(),
  width = 11.8, height = 6, dpi = 600)
```

## Study 3 - MASC

Calculate ANOVA, generate APA style ANOVA table, and plot ggstatsplot.
```{r S3 MASC set1 ANOVA}

# Overall measurements for all participants.

## MASC set 1
jmv::ANOVA(
    formula = MASC_set1 ~ condition,
    data = cleaned_df,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    #emMeans = ~ condition,
    emmTables = TRUE)

ANOVA_study3_MASC1 <- lm(MASC_set1 ~ condition, data = cleaned_df)

ggstatsplot::ggbetweenstats(
    data = cleaned_df,
    y = MASC_set1,
    x = condition,
    originaltheme = TRUE,
    ylab = "MASC - Perceived dishonesty",
    xlab = "Conditions",
    title = "Multi Aspect Scale of Cheating (MASC) - Likelihood of others to behave dishonestly")
```

```{R Study3 MASC1 output, echo=TRUE}
apa.aov.table(ANOVA_study3_MASC1, filename = "Exp3 MASC set1 ANOVA.doc",table.number = 5)
ggsave(
  "MASC1_Dishonesty_plot.png", plot = last_plot(), 
  width = 9, height = 5.5, dpi = 600)
```

```{R MASC set2 ANOVA}
## MASC set 2
jmv::ANOVA(
    formula = MASC_set2 ~ condition,
    data = cleaned_df,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    #emMeans = ~ condition,
    emmTables = TRUE)

ANOVA_study3_MASC2 <- lm(MASC_set2 ~ condition, data = cleaned_df)

ggstatsplot::ggbetweenstats(
    data = cleaned_df,
    y = MASC_set2,
    x = condition,
    originaltheme = TRUE,
    ylab = "MASC - Lie detection",
    xlab = "Conditions",
    title = "Multi Aspect Scale of Cheating (MASC) - Interpreting common excuses as a lie")
```

```{R Study3 set2 output, echo=TRUE}
apa.aov.table(ANOVA_study3_MASC2, filename = "Exp3 MASC set2 ANOVA.doc",table.number = 6)
ggsave(
  "MASC2_Lie_plot.png", plot = last_plot(), 
  width = 9, height = 5.5, dpi = 600)
```

```{R Study 3 MASC set 3 ANOVA}

## MASC set 3
jmv::ANOVA(
    formula = MASC_set3 ~ condition,
    data = cleaned_df,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    #emMeans = ~ condition,
    emmTables = TRUE)

ANOVA_study3_MASC3 <- lm(MASC_set3 ~ condition, data = cleaned_df)

ggstatsplot::ggbetweenstats(
    data = cleaned_df,
    y = MASC_set3,
    x = condition,
    originaltheme = TRUE,
    ylab = "MASC - Predict action in dillemmas",
    xlab = "Conditions",
    title = "Multi Aspect Scale of Cheating (MASC) - Likelihood of actors to behave dishonestly in dilemmas")
```

```{R Study3 MASC Set3 output, echo=TRUE}
apa.aov.table(ANOVA_study3_MASC3, filename = "Exp3 MASC set3 ANOVA.doc",table.number = 7)
ggsave(
  "MASC3_dilemmas_plot.png", plot = last_plot(), 
  width = 9, height = 5.5, dpi = 600)
```

## Study 3 - BIDR
Calculate ANOVA, generate APA style ANOVA table, and plot ggstatsplot.
```{r BIDR self ANOVA}

## BIDR - self deceptive
jmv::ANOVA(
    formula = BIDR_self_deceptive ~ condition,
    data = cleaned_df,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    #emMeans = ~ condition,
    emmTables = TRUE)

ANOVA_study3_BIDR1 <- lm(BIDR_self_deceptive ~ condition, data = cleaned_df)

ggstatsplot::ggbetweenstats(
    data = cleaned_df,
    y = BIDR_self_deceptive,
    x = condition,
    originaltheme = TRUE,
    ylab = "BIDR - self deceptive",
    xlab = "Conditions",
    title = "Balanced Inventory of Desirable Responding - Self Deceptive Score")
```

```{R Study3 BIDR self ouput, echo=TRUE}
apa.aov.table(ANOVA_study3_BIDR1, filename = "Exp3 BIDR1 ANOVA.doc",table.number = 8)
ggsave(
  "BIDR_SelfDeceptive_plot.png", plot = last_plot(), 
  width = 9, height = 5.5, dpi = 600)
```

```{R Study3 BIDR impression ANOVA}
## BIDR - impression management
jmv::ANOVA(
    formula = BIDR_impre_manage ~ condition,
    data = cleaned_df,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    #emMeans = ~ condition,
    emmTables = TRUE)

ANOVA_study3_BIDR2 <- lm(BIDR_impre_manage ~ condition, data = cleaned_df)

ggstatsplot::ggbetweenstats(
    data = cleaned_df,
    y = BIDR_impre_manage,
    x = condition,
    originaltheme = TRUE,
    ylab = "BIDR - impression management",
    xlab = "Conditions",
    title = "Balanced Inventory of Desirable Responding - Impression Management Score")
```

```{R Study3 BIDR impression output, echo=TRUE}
apa.aov.table(ANOVA_study3_BIDR2, filename = "Exp3 BIDR2 ANOVA.doc",table.number = 9)
ggsave(
  "BIDR_ImpressionManagement_plot.png", plot = last_plot(), 
  width = 9, height = 5.5, dpi = 600)

```

# Robustness check - planned contrasts for recall conditions

## Study 1 - planned contrast for ANOVA
```{r S1 planned contrasts}

contrast1 = c(3, 3,-2,-2,-2)
contrast2 = c(1,-1, 0, 0, 0)
# comprehensive data
cleaned_df$condition=factor(cleaned_df$condition)
contrasts(cleaned_df$condition) = cbind(contrast1, contrast2)

#Check
contrasts(cleaned_df$condition)

# ANOVA command
# result in the form of regression
#summary.lm(aov1)

ANOVA_mani_check <- lm(ManiCheck ~ condition, data = cleaned_df)
summary.lm(ANOVA_mani_check)

ANOVA_exp1_DV1 <- lm(Exp1_prob_hiring ~ condition, data = cleaned_df)
summary.lm(ANOVA_exp1_DV1)

ANOVA_exp1_DV2 <- lm(Exp1_loyalty ~ condition, data = cleaned_df)
summary.lm(ANOVA_exp1_DV2)

ANOVA_exp1_DV3 <- lm(Exp1_honesty ~ condition, data = cleaned_df)
summary.lm(ANOVA_exp1_DV3)

ANOVA_exp3_MASC1 <- lm(MASC_set1 ~ condition, data = cleaned_df)
summary.lm(ANOVA_exp3_MASC1)

ANOVA_exp3_MASC2 <- lm(MASC_set2 ~ condition, data = cleaned_df)
summary.lm(ANOVA_exp3_MASC2)

ANOVA_exp3_MASC3 <- lm(MASC_set3 ~ condition, data = cleaned_df)
summary.lm(ANOVA_exp3_MASC3)

ANOVA_exp3_BIDR1 <- lm(BIDR_self_deceptive ~ condition, data = cleaned_df)
summary.lm(ANOVA_exp3_BIDR1)

ANOVA_exp3_BIDR2 <- lm(BIDR_impre_manage ~ condition, data = cleaned_df)
summary.lm(ANOVA_exp3_BIDR2)

```

## Study 2 - planned contrast for repeated ANOVA
```{r S2 planned contrasts}
# Repeated-measures ANOVA with the afex package
library("afex")

# using the long format "df_s2long" created in main analysis:

# planned contrast notation
contrast1 = c(3, 3,-2,-2,-2)
contrast2 = c(1,-1, 0, 0, 0)
df_s2long$condition <- as.factor(df_s2long$condition)
contrasts(df_s2long$condition) = cbind(contrast1, contrast2)

#Check
contrasts(df_s2long$condition)

# ANOVA command
ANOVA_Exp2_DV1 <- afex::aov_car(Exp2_seen_wrong ~ condition*scenario + Error(ID/scenario), data=df_s2DV1)
ANOVA_Exp2_DV2 <- afex::aov_car(Exp2_self_action ~ condition*scenario + Error(ID/scenario), data=df_s2DV2)
ANOVA_Exp2_DV3 <- afex::aov_car(Exp2_guide_other ~ condition*scenario + Error(ID/scenario), data=df_s2DV3)

summary(ANOVA_Exp2_DV1)
summary(ANOVA_Exp2_DV2)
summary(ANOVA_Exp2_DV3)

```

# Planned Additional Analysis
Investigate the order effect if we fail to find support for the original's analyses.

## Study 1 - ANOVA
Only include participants that saw study 1 before study 2.
```{r S1 ANOVA-A}

df_s1 <- cleaned_df %>% filter(study_order == "Exp1First")
write.csv(df_s1, "stimulated_cleaned_study1.csv",fileEncoding = "UTF-8")

# DV1 Probability of hiring the candicate
jmv::ANOVA(
    formula = Exp1_prob_hiring ~ condition,
    data = df_s1,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    #emMeans = ~ condition, # using ggstatsplot instead
    emmTables = TRUE)

ANOVA_exp1_DV1 <- lm(Exp1_prob_hiring ~ condition, data = df_s1)
#apa.aov.table(ANOVA_exp1_DV1, filename = "Exp1 DV1 ANOVA.doc",table.number = 10)

# plot ggstatsplot
ggstatsplot::ggbetweenstats(
    data = df_s1,
    y = Exp1_prob_hiring,
    x = condition,
    originaltheme = TRUE,
    ylab = "Study 1 Likelihood of hiring",
    xlab = "Conditions")
```

```{R S1DV2 A}
# DV2 Perceived loyalty of the candidate
jmv::ANOVA(
    formula = Exp1_loyalty ~ condition,
    data = df_s1,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    #emMeans = ~ condition,
    emmTables = TRUE)

ANOVA_exp1_DV2 <- lm(Exp1_loyalty ~ condition, data = df_s1)
#apa.aov.table(ANOVA_exp1_DV2, filename = "Exp1 DV2 ANOVA.doc",table.number = 11)

# plot ggstatsplot
ggstatsplot::ggbetweenstats(
    data = df_s1,
    y = Exp1_loyalty,
    x = condition,
    originaltheme = TRUE,
    ylab = "Study 1 Perceived Loyalty",
    xlab = "Conditions")
```

```{R S1DV3 A}
# DV3 Perceived honesty of the candidate
jmv::ANOVA(
    formula = Exp1_honesty ~ condition,
    data = df_s1,
    effectSize = "eta",
    modelTest = TRUE,
    homo = TRUE,
    postHocES = "d",
    postHocEsCi = TRUE,
    #emMeans = ~ condition,
    emmTables = TRUE)

ANOVA_exp1_DV3 <- lm(Exp1_honesty ~ condition, data = df_s1)
#apa.aov.table(ANOVA_exp1_DV3, filename = "Exp1 DV3 ANOVA.doc",table.number = 12)

# plot ggstatsplot 
ggstatsplot::ggbetweenstats(
    data = df_s1,
    y = Exp1_honesty,
    x = condition,
    originaltheme = TRUE,
    ylab = "Study 1 Perceived Honesty",
    xlab = "Conditions")

```

## Study 2 - Repeated ANOVA

Only include participants that saw study 2 before study 1.

Pivot to long format for ggstatsplot.
```{r study 2 pivot longer - A}
# add a column of unique participant ID
cleaned_df <- dplyr::mutate(cleaned_df, ID = row_number())

df_s2 <- cleaned_df %>% filter(study_order == "Exp2First")
#write.csv(df_s2, "stimulated_cleaned_study2.csv",fileEncoding = "UTF-8")

#pivot longer
df_s2DV1A <- pivot_longer(df_s2, cols = c(Exp2_S1_seen_wrong, Exp2_S2_seen_wrong_T2),names_to = "scenario",values_to = "Exp2_seen_wrong") 
df_s2DV2A <- pivot_longer(df_s2, cols = c(Exp2_S1_self_action, Exp2_S2_self_action_T2),names_to = "scenario",values_to = "Exp2_self_action") 
df_s2DV3A <- pivot_longer(df_s2, cols = c(Exp2_S1_guide_other, Exp2_S2_guide_other_T2),names_to = "scenario",values_to = "Exp2_guide_other") 

# combine three DVs
df_s2longA <- df_s2DV1A %>% dplyr::select("ID","condition","scenario","Exp2_seen_wrong") %>% dplyr::mutate(Exp2_seen_wrong = as.numeric(Exp2_seen_wrong)) %>%
  cbind(Exp2_self_action = as.numeric(df_s2DV2A$Exp2_self_action)) %>%
  cbind(Exp2_guide_other = as.numeric(df_s2DV3A$Exp2_guide_other))

# rename the scenario variable for plotting 
df_s2longA <- df_s2longA %>% 
  mutate(scenario = case_when(
    scenario == "Exp2_S1_seen_wrong" ~ "Scenario 1 Leaking interview questions",
    scenario == "Exp2_S2_seen_wrong_T2" ~ "Scenario 2 Changing used product"))

```

Study 2 DV1 - Perception of suggested actions as wrong.
```{r S2 DV1 ANOVA A}

jmv::anovaRM(
    data = df_s2,
    rm = list(
        list(
            label="scenario",
            levels=c("S1", "S2"))),
    rmCells = list(
        list(
            measure="Exp2_S1_seen_wrong",
            cell="S1"),
        list(
            measure="Exp2_S2_seen_wrong_T2",
            cell="S2")),
    bs = condition,
    effectSize = "eta",
    rmTerms = ~ scenario,
    bsTerms = ~ condition,
    leveneTest = TRUE,
    #emMeans = ~ scenario:condition,
    emmTables = TRUE,
    groupSumm = TRUE)

# ggstatsplot for condition comparisons in between-subjects designs repeated across all levels of a grouping variable.
# link to tutorial: https://indrajeetpatil.github.io/ggstatsplot/reference/grouped_ggbetweenstats.html

ggstatsplot::grouped_ggbetweenstats(
  data = df_s2longA,
  y = Exp2_seen_wrong,
  x = condition,
  grouping.var = scenario,
  ylab = "Perceived unethicality",
  xlab = "Conditions"
  ) 
```

```{R Study2DV1 plot A, eval=FALSE, include=TRUE}
ggsave(
  "Study2DV1SeenWrong.png", plot = last_plot(),
  width = 11.8, height = 6, dpi = 600)

```

Study 2 DV2 - Likelihood of the self conducting similar behavior.
```{r S2 DV2 ANOVA A}
jmv::anovaRM(
    data = df_s2,
    rm = list(
        list(
            label="scenario",
            levels=c("S1", "S2"))),
    rmCells = list(
        list(
            measure="Exp2_S1_self_action",
            cell="S1"),
        list(
            measure="Exp2_S2_self_action_T2",
            cell="S2")),
    bs = condition,
    effectSize = "eta",
    rmTerms = ~ scenario,
    bsTerms = ~ condition,
    leveneTest = TRUE,
    #emMeans = ~ scenario:condition,
    emmTables = TRUE,
    groupSumm = TRUE)

ggstatsplot::grouped_ggbetweenstats(
  data = df_s2longA,
  y = Exp2_self_action,
  x = condition,
  grouping.var = scenario,
  ylab = "Likelihood of the self conducting suggested behavior",
  xlab = "Conditions"
  ) 

```

```{R Study2DV2 plot A, eval=FALSE, include=TRUE}
ggsave(
  "Study2DV2SelfAction.png", plot = last_plot(),
  width = 11.8, height = 6, dpi = 600)

```

Study 2 DV3 - Likelihood of advising others to perform unethical but self-benefiting behavior.
```{r S2 DV3 ANOVA A}
jmv::anovaRM(
    data = cleaned_df,
    rm = list(
        list(
            label="scenario",
            levels=c("S1", "S2"))),
    rmCells = list(
        list(
            measure="Exp2_S1_guide_other",
            cell="S1"),
        list(
            measure="Exp2_S2_guide_other_T2",
            cell="S2")),
    bs = condition,
    effectSize = "eta",
    rmTerms = ~ scenario,
    bsTerms = ~ condition,
    leveneTest = TRUE,
    #emMeans = ~ scenario:condition,
    emmTables = TRUE,
    groupSumm = TRUE)

ggstatsplot::grouped_ggbetweenstats(
  data = df_s2long,
  y = Exp2_guide_other,
  x = condition,
  grouping.var = scenario,
  ylab = "Likelihood of advising others to behave unethically",
  xlab = "Conditions"
  ) 
```

```{R Study2DV3 plot A, eval=FALSE, include=TRUE}
ggsave(
  "Study2DV3AdviseOthers.png", plot = last_plot(),
  width = 11.8, height = 6, dpi = 600)
```


## Testing order effect as a moderator 
note: the moderator pacakge is not yet available for the current version of R, hence we pasted all code on running moderation analysis from JAMOVI, but will provide the analysis and result in a separate .omv file. 

study 1

```{r S1 moderator, eval=FALSE, include=TRUE}

install.packages("medmod")
library(medmod)
medmod::mod(
    data = cleaned_df,
    dep = Exp1_prob_hiring,
    mod = study_order_n,
    pred = Condition_n,
    ci = TRUE,
    simpleSlopeEst = TRUE,
    simpleSlopePlot = TRUE)

medmod::mod(
    data = cleaned_df,
    dep = Exp1_honesty,
    mod = study_order_n,
    pred = Condition_n,
    ci = TRUE,
    simpleSlopeEst = TRUE,
    simpleSlopePlot = TRUE,
    duplicate = 2)

medmod::mod(
    data = cleaned_df,
    dep = Exp1_loyalty,
    mod = study_order_n,
    pred = Condition_n,
    ci = TRUE,
    simpleSlopeEst = TRUE,
    simpleSlopePlot = TRUE,
    duplicate = 2)

```

study 2

```{r moderator, eval=FALSE, include=TRUE}

medmod::mod(
    data = cleaned_df,
    dep = Exp2_S1_seen_wrong,
    mod = study_order_n,
    pred = Condition_n,
    ci = TRUE,
    simpleSlopeEst = TRUE,
    simpleSlopePlot = TRUE,
    duplicate = 2)

medmod::mod(
    data = cleaned_df,
    dep = Exp2_S1_self_action,
    mod = study_order_n,
    pred = Condition_n,
    ci = TRUE,
    simpleSlopeEst = TRUE,
    simpleSlopePlot = TRUE,
    duplicate = 2)

medmod::mod(
    data = cleaned_df,
    dep = Exp2_S1_guide_other,
    mod = study_order_n,
    pred = Condition_n,
    ci = TRUE,
    simpleSlopeEst = TRUE,
    simpleSlopePlot = TRUE,
    duplicate = 2)

medmod::mod(
    data = cleaned_df,
    dep = Exp2_S2_seen_wrong_T2,
    mod = study_order_n,
    pred = Condition_n,
    ci = TRUE,
    simpleSlopeEst = TRUE,
    simpleSlopePlot = TRUE,
    duplicate = 2)

medmod::mod(
    data = cleaned_df,
    dep = Exp2_S2_self_action_T2,
    mod = study_order_n,
    pred = Condition_n,
    ci = TRUE,
    simpleSlopeEst = TRUE,
    simpleSlopePlot = TRUE,
    duplicate = 2)

medmod::mod(
    data = cleaned_df,
    dep = Exp2_S2_guide_other_T2,
    mod = study_order_n,
    pred = Condition_n,
    ci = TRUE,
    simpleSlopeEst = TRUE,
    simpleSlopePlot = TRUE,
    duplicate = 2)

```
